Irt plot extra

### 2022-02-16 appendix-1.Rmd
Candidate for 2nd round

```{r map}
papaja::apa_table(map3, caption = "Minimum Average Partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
```

@@

mi.desc_table <- CFA.descriptives[,c(1,2,5,6,7)] %>%
  tbl_summary(
    by = slypos_demographics_language.factor,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
  modify_caption("Demographic Characteristics: Native English Speakers")

@@

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minimum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
```

@@

```{r efaunmerged}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
```

@@

```{r EFAsix}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported, Sixth factor has only two salient loadings", longtable =T, font_size = "footnotesize")
```

@@

```{r tztable}
apa_table(tz, longtable =T,font_size = "footnotesize", caption = "Geographical Location of the participants (n =690)")
```

@@

```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30, & 41) had relatively flat information curves ', out.width='100%', out.height='80%'}
knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
```

>>>>

```{r map}
papaja::apa_table(map3, caption = "Minimum average partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
```

@@

mi.desc_table <- CFA.descriptives[,c(1,2,5,6,7)] %>%
  tbl_summary(
    by = slypos_demographics_language.factor,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
  modify_caption("Demographic characteristics: measurement invariance")

@@

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (minimum residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
```

@@

```{r efaunmerged}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
```

@@

```{r EFAsix}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged responses]", note = "Only loading higher than .30 is reported, Sixth factor has only two salient loadings", longtable =T, font_size = "footnotesize")
```

@@

```{r tztable}
apa_table(tz, longtable =T,font_size = "footnotesize", caption = "Geographical location of the participants (n =690)")
```

@@

```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30,41) had relatively flat information curves', out.width='100%', out.height='100%'}
knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
```

### 2022-02-16 manuscript.Rmd
Candidate for 2nd round

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    E[label = 
                    <Factor identification<br/>Scree Plot: 6 Factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
                    ]

@@

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians. The survey took around 15 to 20 minutes and participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks". At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021. 
## Analytic Strategies

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0). In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we collapsed them into one, making it a 5 point Likert type response format. We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`). Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020]. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018]. We also conducted a EFA on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

@@

To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with Weighted Last Square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.

@@

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2). As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

@@

colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item-total corelation")

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}

@@

```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
knitr::include_graphics('Manuscript.figures/efagt.png',dpi =600)

@@

```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =600)

@@

```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis. By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}

@@

```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE}

@@

We developed a self-reported tool to capture different light exposure related behavior and evaluated its psychometric properties using classical test theory and Item Response Theory based analysis.

48 items were generated by an expert panel and  administered to a large sample (n=`r nrow(EFA.descriptives)` to explore the latent structure. Exploratory Factor Analysis revealed a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime"). The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`. As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item. The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).

The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI. Items in those two scales were looking into behaviors related to sleep. As such the similarity index obtained is expected. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.

Lastly, we developed a short-LEBA (18 items) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`). We discarded five items with relatively flat item information curve [I($\theta$) <.20]. IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour. Test information curve also indicated a good coverage of underlying trait continuum with precision.

## Conclusion
"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an EFA. A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 23-item "LEBA" was found reliable and valid. A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18-item scale with  a good range of coverage across the underlying trait continuum. All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior

>>>>

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    E[label = 
                    <Factor identification<br/>Scree plot: 6 factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
                    ]

@@

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians. The survey took around 15 to 20 minutes and participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants needed to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks". At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample). Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

## Analytic Strategies

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0). In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behaviour. In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we collapsed them into one, making it a 5 point Likert type response format. We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`). Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020]. We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018]. We also conducted a EFA on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

@@

To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`). We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner]. However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.

@@

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2)). As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale.

@@

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]. To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Both our EFA and CFA sample size exceeded these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, fig.cap="Top ten countries with highest responses in our survey", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
```

@@

colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item Total Correlation")

@@

```{r EFAplot, fig.align='center', fig.cap='(A) Five factor solution obtained in exploratory factor analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}

@@

```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary descriptives and response pattern of EFA sample'}
knitr::include_graphics('Manuscript.figures/efagt.png',dpi =600)

@@

```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary descriptives and response pattern of CFA sample'}
knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =600)

@@

```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis. By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}

@@

```{r Testinfo, fig.cap="Test information curves (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime", warning=FALSE}

@@

Though there are lots of validated tool to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure. At present there is a dearth of validated tool to measure light exposure related behaviours. In that vein we have developed a subjective self-reported tool that can capture light exposure related behaviour in different dimensions.

Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments. A large scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from large sample (n=`r nrow(EFA.descriptives)` to explore the latent structure. Exploratory factor analysis revealed a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime"). The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`. As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item. The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa(residual.fitm[6,1],2,F)`).

The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI. Items in those two scales were looking into behaviours related to sleep. As such the similarity index obtained is expected. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.

We developed a short-LEBA (18 items) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`). We discarded five items with relatively flat item information curve [I($\theta$) <.20]. IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour. Test information curve also indicated a good coverage of underlying trait continuum with precision.

LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health. All the five factors of LEBA can identify 'problematic' behaviours that are opposed to good light hygiene.

## Conclusion

We developed a novel self-reported subjective tool- "Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour. We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey. Our EFA gave a five solution with 25 items. A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity). A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18-item scale with  a good  coverage across the underlying trait continuum. Hence, we could recommend that LEBA can be used to measure different aspects of light exposure related behaviour.

## Future Direction

Since, LEBA is the first of its kind, estimating convergent validity with other subjective tool was not possible. One way to establish the convergent validity of LEBA is to administer this subjective tool along which some objective measurement tools (e.g. personalised light dosimeter). Though such objective tools do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure. Also,  light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available tools individual have on their disposal. Our analysis did not consider socio-economic status, as we didn't measure it. Investigating the properties of LEBA while considering different socio-economic status would be a valuable addition.
